\begin{cvline}{Summary}
    \cvtext{As a \textbf{Computational Astrophysicist}, I developed a novel Radiation-Hydrodynamic numerical code and used it to unravel the origin of emissions around distant quasars by testing our theoretical models against state-of-the-art observations.}
    \cvtext{As an \textbf{AI enthusiast}, I developed a feedforward model to solve the Riemann problem, which lies at the heart of most hydrodynamics simulations.}
    \cvtext{As a \textbf{skilled High-Performance Computing programmer}, I have been using various parallel computing techniques, such as OpenMP, GPU programming, and MPI, in my projects for the past eight years.}
    \cvtext{As a \textbf{front-end developer}, I started by creating static websites a long time ago. I added a bit of interaction to my projects and landed in creating complex web applications with modern technologies.}
    \cvtext{As a \textbf{back-end developer}, I started with PHP/MySQL, used the ZEND framework as the next step, then moved to less archaic frameworks like Rails and Node/Express. Along the way, I also gained experiences with MongoDB, Redis, and Elasticsearch.}
    \cvtext{As a \textbf{passionate programmer}, I am constantly learning new technologies, ideas, and best practices. I learned to code when I was 11 with Pascal, and since then, I have tried many languages; among them, I consider myself advanced in Python, JavaScript, C, FORTRAN, Shell Scripting, and Ruby. I am looking forward to learning Julia, Go, and Rust next.}
    \cvtext{As a \textbf{team player}, I have experienced various team rules. I held public events with hundreds of participants, managed many star-gazing events, taught astrophysics and programming to high schoolers, supervised undergrad/grad students, assisted university professors, worked as a junior/mid-senior developer, co-founded a startup (Kelasi), and helped an early-stage startup (SCIVVY) to devise a business plan.}
    % \cvtext{I am eager to join a creative, problem-solving team that allows me to develop my skills further and actively learn new technologies and ideas.}
\end{cvline}